\bf Faster Neural Machine Translation Inference

### 2018-01-26 fast-beam/fast-beam.tex
fast beam paper

In fact, we are usually only interested in the argmax class during inference, not the probability. Therefore, we can skip the second iteration over $p$ in Figure~\ref{algo:Fused Kernel} and avoid computing the softmax altogether.

@@

The algorithm was extended from argmax to beam search for n-best classes.

>>>>

@@

In fact, we are usually only interested in the argmax class during inference, not the probability. Therefore, we can skip the second iteration over $p$ and avoid computing the softmax altogether. %, Figure~\ref{algo:Argmax only}.

% \begin{figure} [h]
% \begin{algorithmic}
% \REQUIRE activation vector $p$, bias vector $b$
% 
% \COMMENT{add bias, calculate $argmax$}t
% \FORALL{$p_i$ in $p$}
%   \IF{$p_i + b_i > max$}
%     \STATE $max \gets p_i + b_i$
%     \STATE $argmax \gets i$
%   \ENDIF
% \ENDFOR 
% 
% 
% \RETURN $argmax$ 
% 
% \end{algorithmic}
% \caption{Argmax only}
% \label{algo:Argmax only}
% \end{figure}

It has been shown ??? that using the n-best number of classes, rather than just the best class, improves translation quality. This is a simple extension to the algorithm of Figure~\ref{algo:Fused Kernel}. Unlike the 1-best case, however, the softmax calculation cannot be skipped as the denominator differs for each input.
